Open Software - Restricted Data:  A Suicide/Climate Case Study.

### 2015-12-04 report1_high_level/manuscript.Rmd
some mods

Restrictions around access to data have increased recently in
Australia, especially to the national mortality database after the
discovery of an incident in which researchers at the University of
Queensland School of Population Health, dissatisfied with the time
it was taking the data custodians to provide data, had hacked into
information about deaths in Australia `r citep(bib[["OKeefe2007"]])`.  
The subsequent investigations lead to
a wide ranging modification to the procedures for approval and
provision of these data that make the access much more restricted.

The Replicability Crisis `r citep(bib[["Peng2011"]])` has emerged, reducing public confidence in statements by scientists. The true extent of the problem may turn out to be overstated `r citep(bib[["Jager2014"]])` however the concern should be addressed to avoid the problems a lack of confidence in scientific publications would entail. Appropriate access to data and analytic software addresses this issue.   We investigated available workflow tools for data management and analysis and implemented a range of these products on our server.  This server has enhanced our capacity for experimentation, reviews, revisions and extensions of work in this field.  We present the results of this project and report that it has streamlined access to population health and environmental data for analysis.

## Motivating case study: Climate/suicide

@@

The number of studies that have examined the relationship between suicide and drought is limited. However, many papers explore links between suicide and climate variables other than drought (such as temperature) and there are two major reviews papers available of the literature on climatic influences on suicide `r citep(c(bib[["Dixon2009"]],bib[["Deisenhammer2003b"]]))`. However, very few studies have investigated the "dryer than average conditions" that is drought specifically.

>>>>

Restrictions around access to data have increased recently in
Australia, especially to the national mortality database after the
discovery of an incident in which Australian population health
researcher Dr Stephen Begg, dissatisfied with the time it was taking
the data custodians to provide data, had hacked into information about
deaths in Australia `r citep(bib[["OKeefe2007"]])`.  The subsequent
investigations led to a wide ranging modification to the procedures
for approval and provision of these data that make the access much
more restricted.

The Reproducibility Crisis `r citep(bib[["Peng2011"]])` has emerged,
reducing public confidence in statements by scientists. The true
extent of the problem may turn out to be overstated
`r citep(bib[["Jager2014"]])` however the concern should be addressed
to avoid the problems a lack of confidence in scientific publications
would entail. Appropriate access to data and analytic software
addresses this issue.  We investigated available workflow tools for
data management and analysis and implemented a range of these products
on our server.  This server has enhanced our capacity for
experimentation, reviews, revisions and extensions of work in this
field.  We present the results of this project and report that it has
streamlined access to population health and environmental data for
analysis.

## Motivating case study: Climate and suicide

@@

The number of studies that have examined the relationship between suicide and drought is limited. However, many papers explore links between suicide and climate variables other than drought (such as temperature) and there are two major reviews papers available of the literature on climatic influences on suicide `r citep(c(bib[["Dixon2009"]],bib[["Deisenhammer2003b"]]))`. However, very few studies have investigated drought specifically.
